---
title: "Writing in R Markdown"
author: "Holly Scheer"
date: "2023-03-29"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, packages, include=FALSE}
library(tidyverse)
```

```{r, include=FALSE}
gapminder_1997 <- read_csv("data/gapminder_1997.csv")
```

```{r, include=FALSE}
gapminder_1997
```



This is a document that we are gonna show to the UN






```{r, lifeExp_1997, echo=FALSE}
ggplot(data = gapminder_1997) +
aes(x = gdpPercap, y = lifeExp, color = continent, size = pop/1000000) +
geom_point() +
labs(x = "GDP Per Capita",
y = "Life Expectancy",
title = "Do people in wealthy countries live longer?",
size = "Population (in millions)")
```

```{r, include=FALSE}
nCountries <- gapminder_1997 %>% 
  select(country) %>% 
  n_distinct()

minGDP <- gapminder_1997 %>% 
  summarize(round(min(gdpPercap))) %>% 
  pull() 

maxGDP <- gapminder_1997 %>% 
  summarize(round(max(gdpPercap))) %>% 
  pull()
```

The above plot shows the relationship between GDP per capita and life expectancy for a total of `r nCountries` countries. For this set of countries, economic wealth ranged from a minimum of USD `r minGDP` to a maximum of `r maxGDP` per capita. 


|HEADER1|HEADER2|
|-------|-------|
|row 1, column 1|row 1 column2|
|row 2, column 1|row 2 column2|

|Summary of Data|
|-------|-------|
|Number of Countries|`r nCountries`|
|Minimum GDP per capita|`r minGDP`|
|Maximum GDP per capita|`r maxGDP`|

```{r kabletable}
library(knitr)

gapminder_1997 %>% 
  filter(continent == "Oceania") %>% 
  kable()
```

# Look I Can Make Words Big

Exercise: R Markdown Syntax
* Create a bullet point list with three items
* as the first item, write the name of your current favorite programming language in bold 
* as the second item, write the name of a function you have so far found most useful in italics
* as the third item, write one thing you want to learn next on your porgramming journey in bold italics
* turn your bullet point list into a numbered list 
* create a fourth list item and find an online guide and/or cheat sheet for basic Markdown syntax; write its name down here adn hyperlink its URL

* **R**
* *summarize*
* ***coding syntax***
* file:///Users/scheerh/Downloads/rmarkdown.pdf

1. **R**
1. *summarize*
1. ***coding syntax***
1. [file:///Users/scheerh/Downloads/rmarkdown.pdf] (Great Markdown Guide)

Steps for a git flow:
1. git pull
1. git status 
1. git add
1. git commit -m "message"
4. git push 











